CRUSE to Safe Cycling in Ireland

### 2023-09-20 paper.qmd
Add abbreviations

@@

A feature of active travel interventions is that they require dense networks of routes to be effective [TODO: cite parkin].
This means that high levels of geographic resolution are needed in the data used to estimate cycling potential.
However, datasets on travel patterns are often only available at the level of administrative zones.

@@

>>>>

<!-- Todo: add section on input datasets -->

@@

A feature of active travel interventions is that they require dense networks of routes to be effective [TODO: cite parkin].
This means that high levels of geographic resolution are needed in the data used to estimate cycling potential.
However, datasets on travel patterns are often only available at the level of administrative zones.
The Central Statistics Office (CSO) in Ireland provides Place of Work, School or College Census of Anonymised Records (POWSCAR) data on the number of people travelling to work and school at the Electoral Division (ED) level, for example.

@@

CSO: Central Statistics Office

CRUSE: Cycle Route Uptake and Scenario Estimation

ED: Electoral Division

GTFS: General Transit Feed Specification

KSI: Killed and Seriously Injured

NRA: National Road Authority

NRN: National Road Network

OSM: Open Street Map

PCT: Propensity to Cycle Tool

POWSCAR: Place of Work, School or College Census of Anonymised Records

TII: Transport Infrastructure Ireland
